Generating presidential tweets with an LSTM network

### 2018-04-19 paper/paper.tex
Add TODO notes to paper

\title{Generating haikus with an LSTM network}

\author{
    Austin Gill\\
    Department of Mathematics and Computer Science\\
    South Dakota School of Mines and Technology\\
    Rapid City SD, 57701\\
    \texttt{\href{mailto:austin.gill@mines.sdsmt.edu}{austin.gill@mines.sdsmt.edu}} \\
}

@@

\begin{abstract}
    Here's an abstract.
\end{abstract}

\section{Introduction}
    Here's the introduction.

\section{Stuff}
    Here's some stuff you didn't know!

\section{Conclusion}
    Conclude something\todo{Something useful!}

\end{document}

>>>>

\title{Generating presidential tweets with an LSTM network}

\author{%
    Austin Gill\\
    Department of Mathematics and Computer Science\\
    South Dakota School of Mines and Technology\\
    Rapid City SD, 57701\\
    \texttt{\href{mailto:austin.gill@mines.sdsmt.edu}{austin.gill@mines.sdsmt.edu}}\\
}

@@

\begin{abstract}
    \todoinline{Write an abstract, but after the paper is finished.}
\end{abstract}

\section{Introduction}
    \todoinline{
        \begin{itemize}
            \item Purpose
            \item Background and general research (Haiku paper using word association norms?)
            \item Mention original intent of generating haikus?
            \item Introduce and defend the final model
            \item Introduce the experimental method used to verify the model
        \end{itemize}
    }

\section{Experiments}
    \todoinline{
        \begin{itemize}
            \item Initial attempt based on generation of a large book (inspired by\dots)
            \item Formulation of the input/output/generation data form? (How to sample with some diversity)
            \item Different architectures attempted (Different plots, but the plots are all pngs\dots)
            \item Final architecture inspired by some paper that I have to find
            \item number epochs, optimizer, etc.
        \end{itemize}
    }

\section{Results}
    \todoinline{
        \begin{itemize}
            \item Hack validation data into training and produce plots?
            \item Give example tweets?
            \item Grammar, spelling, etc.
            \item Accuracy is meaningless because you're trying to create \textit{new} tweets. This is where the sampling with diversities comes in. The higher diversity the more creative the network is, but the more meaningless it becomes.
            \item Produce a largeish amount of generated tweets.
        \end{itemize}
    }

\section{Discussion}
    \todoinline{
        \begin{itemize}
            \item How good was it?
            \item Accuracy meaningless because attempt is creative generation.
            \item Did it pick up on patterns backed by data?
        \end{itemize}
    }

\section{Future Work}
    \todoinline{
        \begin{itemize}
            \item Word association norms?
            \item Embeddings?
            \item Combining sources?
            \item Grammar and spelling
            \item GAN
            \item Crowd-sourced adversarial network as a training component?
        \end{itemize}
    }

\bibliographystyle{ieeetr}
% Automatically places a \section*{References}...
\bibliography{paper}
\end{document}
